Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-16 Tex/elsevier/reply Solar Energy JULY 2019.tex
solar energy revised text and reply letter

\begin{resposta} 
We thank the reviewer fot this insightful comment. Indeed, it summarizes what was intended to be studied in this manuscript. Additionally, we have emphasized that the main focus of our study relies on the validation process of solar PV systems instead of the mathematical modelling, which was already investigated in prior studies over the last two decades; this particular information was carefully included in the revised abstract, introduction, and conclusion sections since it was unclear in the previous version of our manuscript. Regarding Figure 2, we fixed it as recommended by the reviewer. Moreover, we applied the same procedure to voltage V, in order to keep consistency throughout our manuscript.

@@

\begin{resposta} 
Note that our options about specialized off-the-shelf tools to design stand-alone solar PV systems are very limited in literature, which motivated us to perform further studies in this area. In particular, as described in Section 2.1, only Hybrid2 and HOMER Pro perform off-grid with battery analysis of PV systems. Hybrid2 is not supported anymore, thereby being in disuse. We have updated this information in our manuscript \textcolor{red}{Which section?}. Therefore, in this particular research field (stand-alone solar PV systems), only HOMER Pro could be used for comparative purposes. However, in our experiments we could some general simulation tools with the same mathematical model adopted by our automated verification tool. However, this would represent an unfair comparison since we would need to tweak the simulation tools to prepare them for comparison purposes, which could introduce errors. We have described this limitation in Section 5.4 (``Threats to Validity'') in order to state that additional comparisons could be carried out with general simulation tools if they employ similar mathematical models as the ones described here.

@@

The information from temperature and solar irradiance from every house location, used by the simulation and formal verification tools, come from historical data collected from real stations, which are available in Weather Base and Energy Plus web sites, as presented in our "References" section \textcolor{red}{could you please indicate the references here? for example, [3, 7, 10]}. Considering that the idea of our study is to show the effectiveness of the proposed verification method just after the design phase (i.e., before deployment), we believe that it is a plausible procedure for not using weather base stations in each place since House 1, House 2, House 3, and House 4 (the ones in a riverside indigenous community) do not have weather station available to collect data and the information must be approximated to Manaus data (the closest municipality with historical data and regular measurement of data). Because of that, we decided to add this discussion in Section ``5.4 Threats to Validity''. We thank you for that specific comment.
\end{resposta}

>>>>

\begin{resposta} 
We thank the reviewer fot this insightful comment. Indeed, it summarizes what was intended to be studied in this manuscript. Additionally, we have emphasized that the main focus of our study relies on the validation process of solar PV systems instead of the mathematical modelling, which was already investigated in prior studies over the last two decades; this particular information was carefully included in the revised abstract, introduction, and conclusion sections since it was unclear in the previous version of our manuscript. Regarding Figure 2, we fixed it as recommended by the reviewer. Moreover, we applied the same procedure to voltage $V$, in order to keep consistency throughout our manuscript.

@@

\begin{resposta} 
Note that our options about specialized off-the-shelf tools to design stand-alone solar PV systems are very limited in literature, which motivated us to perform further studies in this area. In particular, as described in Section 2.1, only Hybrid2 and HOMER Pro perform off-grid with battery analysis of PV systems. Hybrid2 is not supported anymore, thereby being in disuse. We have updated this information in our manuscript (Section 2.1 as well). Therefore, in this particular research field (stand-alone solar PV systems), only HOMER Pro could be used for comparative purposes. However, in our experiments we could use some general simulation tools with the same mathematical model adopted by our automated verification tool. However, this would represent an unfair comparison since we would need to tweak the simulation tools to prepare them for comparison purposes, which could introduce errors. We have described this limitation in Section 5.4 (``Threats to Validity'') in order to state that additional comparisons could be carried out with general simulation tools if they employ similar mathematical models as the ones described here. Moreover, we mentioned the possibility to include this general purpose software tool comparative as future work (Section 6).

@@

The information from temperature and solar irradiance from every house location, used by the simulation and formal verification tools, come from historical data collected from real stations, which are available in Weather Base and Energy Plus web sites, as presented in our "References" section: (Weatherbase, 2018) and (EnergyPlus, 2018). Considering that the idea of our study is to show the effectiveness of the proposed verification method just after the design phase (i.e., before deployment), we believe that it is a plausible procedure for not using weather base stations in each place since House 1, House 2, House 3, and House 4 (the ones in a riverside indigenous community) do not have weather station available to collect data and the information must be approximated to Manaus data (the closest municipality with historical data and regular measurement of data). Because of that, we decided to add this discussion in Section ``5.4 Threats to Validity''. We thank you for that specific comment.
\end{resposta}

### 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1.tex
solar energy revised text and reply letter

\begin{abstract}
\textcolor{red}{With declining costs and increasing performance, the deployment of renewable energy systems is growing faster. In $2017$, for the first time, the number of people without access to electricity dropped down below $1$ billion, but trends on energy access likewise fall short of global goals. Particular attention is given to stand-alone solar photovoltaic (PV) systems in rural areas or where grid extension is unfeasible. Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design-space. Automated verification using model checking has proven to be an effective technique to validate complex (state transition) systems. This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system, including solar panel, charge controller, battery, inverter, and electric load. Our main focus is on the solar PV project validation to be carried out just after the system sizing, i.e., prior to buying equipment and deploying it in the field, as a safe approach to ensure the intended behavior. Case studies, ranging from $253$ W to $814$ W, were used to evaluate this proposed approach and to compare that with specialized simulation tools. Different verification tools were evaluated to compare performance and soundness among automated verifiers. The experimental results reported by our automated verification method and by the simulation tools were compared with data collected from dwellers of the deployed cases, thereby showing the effectiveness of our approach, where specific conditions that lead to failures in a solar PV system are only detailed by the automated verification method.}
\end{abstract}

@@

As highlights, only HOMER and Hybrid2 perform off-grid system with battery backup analysis. \textcolor{red}{Hybrid2 is not supported anymore, being in disuse.} \textcolor{green}{how did you conclude that? explain here...} %all the tools perform solar photovoltaic analysis; 

@@

We have performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}. \textcolor{red}{Power peak, power surge, and energy consumption were estimated based on visiting and survey applied to each house (before the electrification).} %Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.

\begin{table}
\caption{Case studies: stand-alone solar PV systems.}\label{tab2}
\begin{scriptsize}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\hline
Item & House 1 & House 2 & House 3 & House 4 & House 5\\
\hline
\hline
PV Panels &  \multicolumn{4}{|c|}{3$\times$325 W: (3S)} & 4$\times$325 W: (2S-2P) \\
\hline
Batteries & \multicolumn{4}{|c|}{\makecell{4$\times$220 Ah: (2S-2P)\\ autonomy: 48 h}} & \makecell{4$\times$120 Ah (4S)\\ autonomy: 6 h}\\
\hline
Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150 V/35 A}\\
\hline
Inverter & \multicolumn{4}{|c|}{700 W, surge: 1,600 W} & 1,200 W, surge: 1,600 W\\
\hline
\textcolor{red}{Power peak (W)}& 342  & 253  & 263 & 322 & 814 \\
\hline
\textcolor{red}{Power surge (W)}& 342 & 722 & 732 & 896 & 980\\
\hline
\makecell{Consumption \\ kWh/day}& \textcolor{red}{3.9} & \textcolor{red}{3.6} & \textcolor{red}{2.5} & \textcolor{red}{4.3} & \textcolor{red}{4.88} \\
\hline
GPS Coordinates & \multicolumn{4}{|c|}{\makecell{2$^{o}$44'50.0"S 60$^{o}$25'47.8"W\\}} & \makecell{3$^{o}$4'20.208"S \\60$^{o}$0'30.168"W}\\
\hline
Details & \multicolumn{4}{|c|}{\makecell{Riverside indigenous community\\Rural Area of Manaus - Brazil}} & \makecell{Urban house \\Manaus-Amazonas-Brazil}\\
\hline
\hline
\end{tabular}
\textcolor{red}{Legend: (S): Series; (P): Parallel.}
\end{scriptsize}
\end{table}
%------------------------------------------
\subsection{Objectives and Setup}
\label{sec:setup}
%------------------------------------------
\textcolor{red}{We aim} to answer two research questions:
%
\begin{enumerate}
\item[RQ1] \textbf{(soundness)} Does our automated verification approach provide correct results?
\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a simulation commercial tool?
\end{enumerate}

@@

\textcolor{red}{
\textit{Temperature and Solar Irradiance Data}: Information related to temperature and solar irradiance of each case study, independently of using simulation or formal verification, come from databases available online \textcolor{green}{cite them here?}. However, considering that riverside communities do not have weather stations, the data used in our study come from the closest municipality (Manaus in all case studies), where stations collect regularly those data. Therefore, the most accurate should be the use of weather stations in each location to obtain the data.}

@@

As future work, we will \textcolor{red} {expand the number of case studies (preferentially in different countries), and also consider} other types of renewable energy and even hybrid ones to allow our method to verify typical rural electrification.

>>>>

\begin{abstract}
\textcolor{red}{With declining costs and increasing performance, the deployment of renewable energy systems is growing faster. In $2017$, for the first time, the number of people without access to electricity dropped down below $1$ billion, but trends on energy access likewise fall short of global goals. Particular attention is given to stand-alone solar photovoltaic (PV) systems in rural areas or where grid extension is unfeasible. Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design-space. Automated verification using model checking has proven to be an effective technique to validate complex (state transition) systems. This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system, including solar panel, charge controller, battery, inverter, and electric load. Our main focus is on the solar PV project validation to be carried out just after the system sizing, i.e., prior to buying equipment and deploying it in the field, as a safe approach to ensure the intended behavior. Case studies, ranging from $253$ W to $814$ W, were used to evaluate this proposed approach and to compare that with specialized simulation tool. Different verification tools were evaluated to compare performance and soundness among automated verifiers. The experimental results reported by our automated verification method and by the simulation tool were compared with data collected from dwellers of the deployed cases, thereby showing the effectiveness of our approach, where specific conditions that lead to failures in a solar PV system are only detailed by the automated verification method.}
\end{abstract}

@@

As highlights, only HOMER and Hybrid2 perform off-grid system with battery backup analysis. \textcolor{red}{Hybrid2 is not supported anymore, being in disuse since that not work on Windows platforms later than Windows XP~\citep{UMASS, Pinho}.} %all the tools perform solar photovoltaic analysis; 

@@

We have performed five case studies to evaluate the proposed approach as described in Table~\ref{tab2}. \textcolor{red}{Power peak, power surge, and energy consumption were estimated based on visiting and survey applied to each house in June 2017 (before the electrification).} %Furthermore, three start-of-art verification tools, as described in Section~\ref{sec:AutomatedVerification} (ESBMC, CBMC, and CPAchecker), and HOMER Pro simulation tool were used to compare the approach effectiveness and efficiency.

\begin{table}
\caption{Case studies: stand-alone solar PV systems.}\label{tab2}
\begin{scriptsize}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
\hline
Item & House 1 & House 2 & House 3 & House 4 & House 5\\
\hline
\hline
PV Panels &  \multicolumn{4}{|c|}{3$\times$325 W: (3S)} & 4$\times$325 W: (2S-2P) \\
\hline
Batteries & \multicolumn{4}{|c|}{\makecell{4$\times$220 Ah: (2S-2P)\\ autonomy: 48 h}} & \makecell{4$\times$120 Ah: (4S)\\ autonomy: 6 h}\\
\hline
Charge Controller & \multicolumn{5}{|c|}{With MPPT of 150 V/35 A}\\
\hline
Inverter & \multicolumn{4}{|c|}{700 W, surge: 1,600 W} & 1,200 W, surge: 1,600 W\\
\hline
\textcolor{red}{Power peak (W)}& 342  & 253  & 263 & 322 & 814 \\
\hline
\textcolor{red}{Power surge (W)}& 342 & 722 & 732 & 896 & 980\\
\hline
\makecell{\textcolor{red}{Consumption}\\ \textcolor{red}{(kWh/day)}}& \textcolor{red}{3.9} & \textcolor{red}{3.6} & \textcolor{red}{2.5} & \textcolor{red}{4.3} & \textcolor{red}{4.88} \\
\hline
GPS Coordinates & \multicolumn{4}{|c|}{\makecell{2$^{o}$44'50.0"S 60$^{o}$25'47.8"W\\}} & \makecell{3$^{o}$4'20.208"S \\60$^{o}$0'30.168"W}\\
\hline
Details & \multicolumn{4}{|c|}{\makecell{Riverside indigenous community\\Rural Area of Manaus - Brazil}} & \makecell{Urban house \\Manaus-Amazonas-Brazil}\\
\hline
\hline
\end{tabular}
\textcolor{red}{Legend: (S): Series; (P): Parallel.}
\end{scriptsize}
\end{table}
%------------------------------------------
\subsection{Objectives and Setup}
\label{sec:setup}
%------------------------------------------
\textcolor{red}{We aim} to answer two research questions:
%
\begin{enumerate}
\item[RQ1] \textbf{(soundness)} Does our automated verification approach provide correct results?
\item[RQ2] \textbf{(performance)} How do the verifiers compare to each other and to a simulation commercial tool?
\end{enumerate}

@@

\textcolor{red}{
\textit{Temperature and Solar Irradiance Data}: Information related to temperature and solar irradiance of each case study, independently of using simulation or formal verification, come from databases available online~\citep{Temperature, Irradiance}. However, considering that riverside communities do not have weather stations, the data used in our study come from the closest municipality (Manaus in all case studies), where stations collect regularly those data. Therefore, the most accurate should be the use of weather stations in each location.}

@@

As future work, we will \textcolor{red} {expand the number of case studies (preferentially in different countries), develop the code of a general purpose simulation tool to include in the comparative, and also consider} other types of renewable energy and even hybrid ones to allow our method to verify typical rural electrification.
